### 2016-08-26 ms/ms.tex
made marilia's comments

\begin{abstract} %% Lauren - I would invert the phrase just so it does not beging with metwork structure - "communities' ability to maintain function in the face of species extinction is related to the structure fo networks". 
  The structure of networks is related to ability of communities to
  maintain function in the face of species extinction. Understanding
  network structure and how it relates to network assembly, therefore,
  is a priority for system-level conservation biology. We explore how the
  assembly of plant-pollinator communities occured, on native plant
  restorations in the Central Valley of California. Species are highly
  dynamic in their positions in the networks, resulting in a community 
  assembly punctuated by significant reorganizations of
  interactions. Non-assembling mature hedgerows and weedy field
  margins did not undergo as many significant network reorganizations, suggesting
  environmental factors alone cannot account for the changes observed
  in assembling communities. Pollinator species were highly
  opportunistic, and in fact the most persistent and generalized
  species were most variable in their network positions --- the
  opposite of what would be expected by preferential attachment. High
  species and interaction turnover was ubiquitous across assembling
  and non-assembling communities, though unique interactions turnover
  at higher rates in assembling hedgerows as the networks continually
  reorganize. Nestedness of assembling networks also increased through
  time, but there was no increase in robustness to simulated plant
  extinctions. The resilience of networks to cascading perturbations,
  however, increased as the communities assembled, at least partially
  due to accumulating species richness. Our results elucidate some of
  the mechanisms underlying plant-pollinator network assembly and
  restoration, while providing further evidence that hedgerows are a
  valuable tool for promoting species conservation and ecosystem
  provision in agricultural areas.
\end{abstract}

@@

%% restoration
%% Lauren, I would combine this paragraph with the next one, because is too short. I tried to think of stuff to add, but I coulnd't...
Understanding network assembly is particularly relevant to ecological
restoration, which is essentially 'applied succession'
\citep[e.g.,][]{parker1997scale}. In pollination systems, the time
since an area was restored has been shown to affect the structure of
networks \citep{forup-2008-742, forup2008restoration,
  devoto2012understanding}, suggesting interactions are evolving as
the community develops. Understanding the mechanisms of network
assembly will help to guide community restoration.

%% restoration of ecosystem services is really important, particularly
%% in ag. but ag is a bad place for pollinators
Facilitating network restoration is especially imperative in areas
where species interactions provide essential ecosystem services, such
as crop pollination. In intensively managed agricultural landscapes,
the demand for pollination services is the greatest
\citep{kremen-2008-10}. However, honey bees, managed extensively
around the world to provide crop pollination, are in global decline
\citep{neumann-2010-1, van-engelsdorp-2009-e6481}. In addition, native
pollinators, which are capable of providing sufficient crop
pollination \citep{kremen-2002-16816, winfree-2007-1105,
  kremen-2004-1109}, are in short supply because these landscapes make
poor habitats for pollinator populations \citep{kremen-2002-16816}. To
ensure the continued provision of ecosystem services and
curb biodiversity loss, it is critical to effective restore pollinators and their
interactions in agricultural landscapes.

@@

%% Lauren I would put 10 year dataset; and I *loved* the way you organized the ideas here!! 
We explore the process of network development using a long-term dataset of plant-pollinator communities assembling following hedgerow restoration in the highly simplified and
intensively managed agricultural landscape of California's Central
Valley.  We first determine whether the mechanism underlying network assembly is a
smooth build up of interactions as would be predicted by preferential
attachment, or punctuated by significant reorganizations of
interactions (i.e., network changing points). Even with changing
points in interaction organization, networks could still be assembling
via preferential attachment if the network reorganizations were
primarily driven the by peripheral, temporally variable species while
a stable, well-connected core of species persist. We test whether the
species are most variable in their network position --- and thus
important contributors network reorganizations --- are less persistent
and connected species. To further explore the mechanisms underlying
the temporal dynamics in the networks, we examine patterns in the
species and interaction temporal turnover. Lastly, we investigate
whether networks are assembling toward predictable interaction
patterns, and the ramifications for the robustness of the networks to
species extinction and cascading perturbations.

@@

We surveyed plant-pollinator interaction networks of assembling
hedgerows communities (N=5), as well as in two types of non-assembling communities
to serve as controls: unrestored, weedy field margins (N=19) and
established hedgerows (greater than 10 years since planting,
N=29). The sites were located in the Central Valley of California in
Yolo, Colusa and Solano Counties. This area is composed of intensively
managed agriculture --- primarily monocultures of conventional row
crops, vineyards and orchards. Hedgerows we planted along field
margins where they do not remove valuable land from
production. Plantings are between are ca.~3--6 m wide and
approximately 350 m long, bordering large (ca.\ 30--hectare) crop
fields. Hedgerows consist of native, perennial, shrub and tree
plantings including \textit{Rosa californica}, \textit{Cercis
  occidentalis}, \textit{Ceanothus spp.}, \textit{Heteromeles
  arbutifolia}, \textit{Sambucus mexicana}, \textit{Eriogonum spp.},
\textit{Baccharis spp.}, \textit{Salvia spp}. and others
\citep{kremen-2015-602, mgonigle-2015-x}. The mean distance between
monitoring sites was 15 km, and the minimum distance between sites of
the same type sampled in the same year was 2 km.  The entire area
surveyed spanned almost 300 km$^2$. The crop fields adjacent to all
sites were similarly managed as intensive, high-input monoculture.

@@

To further elucidate the nature of the change points, we examine the
characteristics of the species that contributed to interaction
reorganization. Some species remain in relatively similar network
positions through time, whereas others are more variable in their position
and thus contribute more strongly to network reorganization. We test
whether the more persistent species with the highest degree (number of interactions) are the
most stable in their network positions, as would be expected if the
networks were assembling via preferential attachment.

@@

%% Lauren I like this paragraph, but I think we could use a figure in the supplementary to help the reader understand... maybe a schematic representation? I'll try and think of something 
Though species may turnover across years, some groups of species may
essentially replace each other if they fill similar roles in the
network, ocupying the same network position and interacting with similar species. At non-assembling communities, species turnover may
overestimate the temporal changes in the networks if the interactions
occurring in one year are similar to those in the next year when they
are weighted by the similarity of their constituent species. We
develop a method examine the temporal turnover of interactions
weighted based on their similarity. We followed \cite{ahn2010link}
algorithm to hierarchically cluster all the interactions (edges)
across sites and years based on their similarity, and build a
dendrogram. The interaction similarity is based how may plants and
pollinators (vertices) two edges share \citep{ahn2010link,
  kalinka2011linkcomm}. The more species edges shared in common, the
shorter the branch length between them on the dendrogram.  We next
calculated the temporal turnover of interactions weighted by their
similarity, as approximated by ``phylogenetic'' distance
\citep{graham2008phylogenetic, picante-2010-1463}. When then use
linear models to test whether the weighted turnover of interactions
varied between assembling and non-assembling networks \citep{lme4,
  lmetest}.

@@

\subsection*{Network structure}
Any changing points in network structure may contribute to the
reorganization of the assembling networks into predictable interaction
patterns. Pollination networks exhibit two main structural patterns
--- modularity \citep[e.g.,][]{Olesen2007} and nestedness
\citep[e.g.,][]{Bascompte2006, Bascompte2003}. In modular networks,
interactions are insular, occurring within separate groups or
``modules'' more often than between modules. Modules in the network
may fragment as the network assembles, enhancing
modularity. Conversely, nested networks are like a pyramid of
interactions, where there are some species that interact with many
species, other species that interact with a subset of those species,
and so on. If species entering the network tend to interact with the
generalist base of the network pyramid as would be expected with
preferential attachment, nestedness would increase through time. The
connectance --- the proportion of observed out of possible
interactions --- would decrease as new, specialist species,
preferentially attach to the core. \flagged{Is this true? - I think that the relationship between richness and connectance is not clear, i changed to decrease because it makes more sense via preferential attachment - the denominator increases because spp are being added, but the number of links does not, because they are specialists --- I checked with Paulo and he agrees} Lastly, the overall level of
network specialization may change as the community assembles. Network-level
specialization will increase if
specialist species colonize the network or species begin to limit
their interaction niche breath as the network assembles  \citep{bluthgen-2006-9}.

@@

We show that the temporal assembly of plant-pollinator networks
following restoration is a highly dynamic process where interactions
often undergo significant reorganizations, the so called changing points. These network organizations
are unlikely a product of environmental forces alone because the
network changing points in non-assembling communities are less
frequent, and few consistent trends in when change points occurred
across all sites. Several sites had network changing points between
years 2009 and 2011 (Fig.~\ref{fig:changePoints}). In California, 2011
marked the beginning of a multi-year drought. The assembling hedgerows
were not sampled in 2010, so disentangling whether the changing points
are due to skipping a year of assembly or the drought is not
possible. Interestingly, most assembling hedgerows did not undergo a
significant interaction reorganization immediately after a hedgerow
was planted (i.e., the transition from weedy field margin to
hedgerow). This result is consistent with the finding that in our
study system, hedgerow restoration takes several years to have an
impact on the plant-pollinator communities (Kremen and M'Gonigle, in
prep).

In addition to finding multiple network organization changing points
during assembly, the way in which these reorganizations occur was different from what is expected by preferential attachment. Based on a preferential attachment mechanism \flagged{process instead of mechanism?}, we expect that the most persistent and high degree species would remain
stable in the network core during assembly. Surprisingly, however, we
encountered the opposite pattern. For example, the five most
ubiquitous species in our study landscape --- \textit{Halictus
  ligatus}, \textit{Halictus tripartitus}, \textit{Lasioglossum
  (Dialictus) incompletum}, and \textit{Toxomerus marginatus} --- were
the only species that changed which module (i.e., community)
they were a member across years in all the assembling
hedgerows. Because species degree and persistence were strongly
correlated, it is difficult to disentangle the causal mechanism for
why species with those characteristics are so variable in their
network position. Generalized species may be able to better exploit
the limited floral resources in the intensively managed agriculture
landscape, and thus also be the most persistent. More persistent species usually 
have longer phenologies, so they can visit many different flowers,
resulting in a higher degree. Either way, our result suggests that
adaptable species can change their network position to utilize the
most advantageous floral resources available, which may depend on the
other pollinator species that are present, and the state of the plant
community. Thus given the opportunity and ability to use different
resources, species will often change their network positions.

@@

When we look at the network-level metrics to explore the mechanism through which the community is assembling, we encounter that nestedness did increase with years
post-restoration, as would be expected if colonizing, specialist
species attached to a central, generalist core
\citep{albrecht2010plant}, as predicted by preferential attachment. In addition, connectance decreased, as would be expected if the network is being colonized by specialist species and the overall mean number of interactions per species did not change. With preferential attachment, however, we
would also expect specialization to increase, and we
found no such trend. Furtheremore, the frequent changing points in network organization, dynamic nature
of species positions in the networks, and turnover of species and
interactions all point to an assembly mechanism other than
preferential attachment.  The stable level of network-level
specialization through the assembly process may be due to the
increased colonization of specialized species \citep{mgonigle-2015-x}
accompanied by an increase in the diet breath of resident
species. This would be expected if resident species were able to
minimize their foraging time by expanding their diet breath as plant
diversity increases with hedgerow maturation \citep{Waser1996,
  pyke1984optimal, Bluthgen2007, albrecht2010plant}. Such a change in
pollinator behavior would also explain the increase in network
nestedness.

>>>>

\begin{abstract}  
  The ability of communities to maintain function in the face of
  species extinction is related to the structure of
  networks. Understanding network structure and how it relates to
  network assembly, therefore, is a priority for system-level
  conservation biology. Using a long-term data set comprising nearly
  20,000 pollinator visitation records, we explore the assembly of
  plant-pollinator communities at native plant restorations in the
  Central Valley of California. Species are highly dynamic in their
  positions in the networks, causing assembly to be punctuated by
  significant reorganizations of interactions. Non-assembling mature
  hedgerows and weedy field margins did not undergo as many
  significant network reorganizations, suggesting environmental
  factors alone cannot account for the changes observed in assembling
  communities. Pollinator species were opportunistic in the flowers
  they visited, and in fact the most persistent and generalized
  species were most variable in their network positions --- the
  opposite of what would be expected by preferential attachment. High
  species and interaction turnover was ubiquitous across assembling
  and non-assembling communities, though unique interactions turnover
  at higher rates in assembling hedgerows as the networks continually
  reorganize. Nestedness of assembling networks also increased through
  time, but there was no increase in robustness to simulated plant
  extinctions. The resilience of networks to cascading perturbations,
  however, increased as the communities assembled, at least partially
  due to accumulating species richness. Our results elucidate some of
  the mechanisms underlying plant-pollinator network assembly and
  restoration, while providing further evidence that hedgerows are a
  valuable tool for promoting species conservation and ecosystem
  provision in agricultural areas.
\end{abstract}

@@

%% restoration
Understanding network assembly is particularly relevant to ecological
restoration, which is essentially 'applied succession'
\citep[e.g.,][]{parker1997scale}. In pollination systems, the time
since an area was restored has been shown to affect the structure of
networks \citep{forup-2008-742, forup2008restoration,
  devoto2012understanding}, suggesting interactions are evolving as
the community develops. Understanding the mechanisms of network
assembly will help to guide community restoration. Facilitating
network restoration is especially imperative in areas where species
interactions provide essential ecosystem services, such as crop
pollination. In intensively managed agricultural landscapes, the
demand for pollination services is the greatest
\citep{kremen-2008-10}. However, honey bees, managed extensively
around the world to provide crop pollination, are in global decline
\citep{neumann-2010-1, van-engelsdorp-2009-e6481}. In addition, native
pollinators, which are capable of providing sufficient crop
pollination \citep{kremen-2002-16816, winfree-2007-1105,
  kremen-2004-1109}, are in short supply because these landscapes make
poor habitats for pollinator populations \citep{kremen-2002-16816}. To
ensure the continued provision of ecosystem services and curb
biodiversity loss, it is critical to restore pollinators and their
interactions in agricultural landscapes.

@@

%% Lauren I would put 10 year dataset; and I *loved* the way you
%% organized the ideas here!!
We explore the process of network development using a nine year
dataset of plant-pollinator communities assembling following hedgerow
restoration in the highly simplified and intensively managed
agricultural landscape of California's Central Valley.  We first
determine whether the mechanism underlying network assembly is a
smooth build up of interactions as would be predicted by preferential
attachment, or punctuated by significant reorganizations of
interactions (i.e., network changing points). Even with changing
points in interaction organization, networks could still be assembling
via preferential attachment if the network reorganizations were
primarily driven the by peripheral, temporally variable species while
a stable, well-connected core of species persist. We test whether the
species are most variable in their network position --- and thus
important contributors network reorganizations --- are less persistent
and connected species. To further explore the mechanisms underlying
the temporal dynamics in the networks, we examine patterns in the
species and interaction temporal turnover. Lastly, we investigate
whether networks are assembling toward predictable interaction
patterns, and the ramifications for the robustness of the networks to
species extinction and cascading perturbations.

@@

We surveyed plant-pollinator interaction networks of assembling
hedgerows communities (N=5), as well as in two types of non-assembling
communities to serve as controls: unrestored, weedy field margins
(N=19) and mature hedgerows (greater than 10 years since planting,
N=29). The sites were located in the Central Valley of California in
Yolo, Colusa and Solano Counties. This area is composed of intensively
managed agriculture --- primarily monocultures of conventional row
crops, vineyards and orchards. Hedgerows we planted along field
margins where they do not remove valuable land from
production. Plantings are between are ca.~3--6 m wide and
approximately 350 m long, bordering large (ca.\ 30--hectare) crop
fields. Hedgerows consist of native, perennial, shrub and tree
plantings including \textit{Rosa californica}, \textit{Cercis
  occidentalis}, \textit{Ceanothus spp.}, \textit{Heteromeles
  arbutifolia}, \textit{Sambucus mexicana}, \textit{Eriogonum spp.},
\textit{Baccharis spp.}, \textit{Salvia spp}. and others
\citep{kremen-2015-602, mgonigle-2015-x}. The mean distance between
monitoring sites was 15 km, and the minimum distance between sites of
the same type sampled in the same year was 2 km.  The entire area
surveyed spanned almost 300 km$^2$. The crop fields adjacent to all
sites were similarly managed as intensive, high-input monoculture.

@@

To further elucidate the nature of the change points, we examine the
characteristics of the species that contributed to interaction
reorganization. Some species remain in relatively similar network
positions through time, whereas others are more variable in their
position and thus contribute more strongly to network
reorganization. We test whether the more persistent species with the
highest degree (number of different interaction parteners) are the
most stable in their network positions, as would be expected if the
networks were assembling via preferential attachment.

@@

%% Lauren I like this paragraph, but I think we could use a figure in
%% the supplementary to help the reader understand... maybe a
%% schematic representation? I'll try and think of something
Though species may turnover across years, some groups of species may
essentially replace each other if they fill similar roles in the
network, ocupying the same network position and interacting with
similar species. At non-assembling communities, species turnover may
overestimate the temporal changes in the networks if the interactions
occurring in one year are similar to those in the next year when they
are weighted by the similarity of their constituent species. We
develop a method examine the temporal turnover of interactions
weighted based on their similarity. We followed \cite{ahn2010link}
algorithm to hierarchically cluster all the interactions (edges)
across sites and years based on their similarity, and build a
dendrogram. The interaction similarity is based how may plants and
pollinators (vertices) two edges share \citep{ahn2010link,
  kalinka2011linkcomm}. The more species edges shared in common, the
shorter the branch length between them on the dendrogram.  We next
calculated the temporal turnover of interactions weighted by their
similarity, as approximated by ``phylogenetic'' distance
\citep{graham2008phylogenetic, picante-2010-1463}. When then use
linear models to test whether the weighted turnover of interactions
varied between assembling and non-assembling networks \citep{lme4,
  lmetest}.

@@

\subsection*{Network structure}
Any changing points in network structure may contribute to the
reorganization of the assembling networks into predictable interaction
patterns. Pollination networks exhibit two main structural patterns
--- modularity \citep[e.g.,][]{Olesen2007} and nestedness
\citep[e.g.,][]{Bascompte2006, Bascompte2003}. In modular networks,
interactions are insular, occurring within separate groups or
``modules'' more often than between modules. Modules in the network
may fragment as the network assembles, enhancing
modularity. Conversely, nested networks are like a pyramid of
interactions, where there are some species that interact with many
species, other species that interact with a subset of those species,
and so on. If species entering the network tend to interact with the
generalist base of the network pyramid as would be expected with
preferential attachment, nestedness would increase through time. The
connectance --- the proportion of observed out of possible
interactions --- would decrease as new, specialist species,
preferentially attach to the core.  Lastly, the overall level of
network specialization may change as the community
assembles. Network-level specialization will increase if specialist
species colonize the network or species begin to limit their
interaction niche breath as the network assembles
\citep{bluthgen-2006-9}.

@@

We show that the temporal assembly of plant-pollinator networks
following restoration is a highly dynamic process where interactions
often undergo significant reorganizations, the so called changing
points. These network reorganizations are unlikely a product of
environmental forces alone because the network changing points in
non-assembling communities are less frequent, and few consistent
trends in when change points occurred across all sites. Several sites
had network changing points between years 2009 and 2011
(Fig.~\ref{fig:changePoints}). In California, 2011 marked the
beginning of a multi-year drought. The assembling hedgerows were not
sampled in 2010, so disentangling whether the changing points are due
to skipping a year of assembly or the drought is not
possible. Interestingly, most assembling hedgerows did not undergo a
significant interaction reorganization immediately after a hedgerow
was planted (i.e., the transition from weedy field margin to
hedgerow). This result is consistent with the finding that in our
study system, hedgerow restoration takes several years to have an
impact on the plant-pollinator communities (Kremen and M'Gonigle, in
prep).

In addition to finding multiple network organization changing points
during assembly, the way in which these reorganizations occur was
different from what is expected by preferential attachment. Based on a
preferential attachment process, we expect that the most persistent
and high degree species would remain stable in the network core during
assembly. Surprisingly, however, we encountered the opposite
pattern. For example, the five most ubiquitous species in our study
landscape --- \textit{Halictus ligatus}, \textit{Halictus
  tripartitus}, \textit{Lasioglossum (Dialictus) incompletum}, and
\textit{Toxomerus marginatus} --- were the only species that changed
which module (i.e., community) they were a member across years in all
the assembling hedgerows. Because species degree and persistence were
strongly correlated, it is difficult to disentangle the causal
mechanism for why species with those characteristics are so variable
in their network position. Generalized species may be able to better
exploit the limited floral resources in the intensively managed
agriculture landscape, and thus also be the most persistent. More
persistent species usually have longer phenologies, so they can visit
many different flowers, resulting in a higher degree. Either way, our
result suggests that adaptable species can change their network
position to utilize the most advantageous floral resources available,
which may depend on the other pollinator species that are present, and
the state of the plant community. Thus given the opportunity and
ability to use different resources, species will often change their
network positions.

@@

When we explore the how the network-level interaction patterns changed
through time, we found that nestedness did increase as the community
assembled, as would be expected if colonizing, specialist species
preferentially attached to a central, generalist core
\citep{albrecht2010plant}. In addition, connectance decreased, as
would be expected if the network is being colonized by specialist
species and the overall mean number of interactions per species did
not change. With preferential attachment, however, we would also
expect specialization to increase, and we found no such
trend. Furtheremore, the frequent changing points in network
organization, dynamic nature of species positions in the networks, and
turnover of species and interactions all point to an assembly
mechanism other than preferential attachment.  The stable level of
network-level specialization through the assembly process may be due
to the increased colonization of specialized species
\citep{mgonigle-2015-x} accompanied by an increase in the diet breath
of resident species. This would be expected if resident species were
able to minimize their foraging time by expanding their diet breath as
plant diversity increases with hedgerow maturation \citep{Waser1996,
  pyke1984optimal, Bluthgen2007, albrecht2010plant}. Such a change in
pollinator behavior would also explain the increase in network
nestedness. Because so many mechanisms give rise to the same patterns
of interaction, additional tests are necessary assess the contribution
of different mechanisms to community assembly.
